Is it time for an NBA expansion?

### 2024-04-12 paper/paper.qmd
Created New Graphs

---
title: "Is it time for an NBA expansion?"
subtitle: "My subtitle if needed"
author: 
  - Yan Mezhiborsky
thanks: "Code and data are available at: ."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

  # Combine with the main data frame
  combined_data <- bind_rows(combined_data, yearly_data)
}
#Remove Less important columns
full_nba_data <- combined_data %>% select(-"G", -"MP", -"2P", -"2PA", -"2P%")

@@

exp_year <- c(1988, 1989, 1995, 2004)

@@

>>>>

---
title: "Is it time for an NBA expansion?"
subtitle: "My subtitle if needed"
author: 
  - Yan Mezhiborsky
thanks: "Code and data are available at: https://github.com/Mezhi18/NBAExpansion ."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

  # Combine with the main data frame
  combined_data <- bind_rows(combined_data, yearly_data)
}
#Remove Less important columns
full_nba_data <- combined_data %>% select(-"G", -"MP", -"2P", -"2PA", -"2P%", -"Rk")

@@

exp_year <- c(1988, 1989, 1995, 2004) #Exansion Year

@@

current_nba_data_long <- nba_data %>%
  filter(Year >= 2004) %>%  # Keep only years from 2004 onwards
  pivot_longer(cols = c(AST, TRB, PTS, STL, BLK), names_to = "Statistic", values_to = "Value")

current_plot <- ggplot(current_nba_data_long, aes(x = Year, y = Value)) +
  geom_point(color = "black") +  # All points in black
  geom_smooth(method = "lm", aes(color = Statistic), se = FALSE) +  # Lines of best fit with different colors
  scale_color_manual(values = line_colors) +
  facet_wrap(~Statistic, scales = "free_y") +  # Facet by statistic, with free y scales
  labs(title = "NBA Stats Over Years (Post-2004)", x = "Year", y = "Value") +
  theme_minimal() +
  theme(legend.position = "none")

current_plot
```
